State of the Art Review on Privacy-Preserving Signatures, Credentials, and Authentication

### 2021-11-17 prism-backend/research/soa_review/ac.tex
Review of BCC+09.

@@

>>>>

\item[\cite{bcc+09}:] This is mostly a theoretical work, which is relevant
  since it is (one of) the first to propose a delegatable anonymous
  credentials systems. The building blocks are randomizable proofs of
  knowledge that randomize both the proof and the statement (which the authors
  build on top of Groth-Sahai proofs), and message authenticators (a variant
  of signatures that require a special notion of unforgeability). Each user
  can create pseudonyms, which are commitments to his secret key, and use
  these commitments to prove ownership of and delegate credentials. These
  pseudonyms are essentially as in the CL line of work (user with pseudonym
  $N^A_U$ w.r.t. organization $A$ and $^B_U$ w.r.t. orgainzation $B$, can
  prove to $B$ (resp. $A$) that $N^A_U$ and $N^B_U$ are related to the
  same secret key). Delegations here follow a sequential order: i.e., if
  a credential has level $L$, then its owner can further delegate this
  credential, and the result would be a credential with level $L+1$. To
  delegate, essentially, the delegator (with pseudonym $N_I$) and delegatee
  (with pseudonym $N_D$) perform an interactive protocol
  through which the delegatee receives a randomizable NIZKP that lets him
  prove knowledge of an authenticator over $N_D$, issued by $N_I$. Since
  both the proof and the statement can be randomized, verifiers do not
  learn the chain of delegation.  Although this is informally mentioned,
  ``attributes'' can be added to the delegation process too (besides to the
  credentials themselves). This is suggested by adding the attributes -- which
  would be visible to the verifier -- to the application of a hash function
  used to derive the authenticator). 

@@

\item[\cite{bcc+09}:] The article follows a game-based definition approach,
  with two security properties (besides correctness): anonymity and
  unforgeability, which are the usual, but extended to the scenario with
  delegation. Basically, the anonymity (in the ideal/real world paradigm)
  property requires that the adversary should not distinguish real credentials
  from simulated ones. Moreover, the adversary should not learn the delegation
  chain of an honest credential (even if it was issued by himself). For
  unforgeability, the requirement is that the adversary should not create
  a delegation chain that includes a delegation by an honest user, if the
  user did not actually perform that delegation.
